Presheaf Model for Dependent Types

### 2017-09-29 papers/talk-11/paper-11.tex
Update paper11
Fix typos

The second projection $\mathbf{q}$ here is the one that models the variables in
an extended context. The application of it returns the current term that
substitutes the variable. Note the similarity to the variable rule in the ccc
model of STLC, as it is also modeled by a second projection there.

@@

Lastly, we need projection morphisms to be defined:
\[
  (\mathbf{p}(w))(I, \rho) = a
\]
\[
  (\mathbf{q}(w)(I, \rho) = b
\]
where $w(I, \rho) = (a, b)$.

\begin{lemma}
  CwF associated to a presheaf category supports $\Sigma$-types.
  \begin{proof}
    Follows after verification of $\Sigma$-rules. A detailed proof is found in
    \cite{Hofmann}.
  \end{proof}
\end{lemma}

>>>>

The second projection $\mathbf{q}$ here is the one that models the variables in
an extended context. The application of it returns the current term for the
variable. Note the similarity to the variable rule in the ccc model of STLC, as
it is also modeled by a second projection there.

@@

Lastly, we need projection morphisms to be defined:
\[
  (\mathbf{p}(w))(I, \rho) = a
\]
\[
  (\mathbf{q}(w))(I, \rho) = b
\]
where $w(I, \rho) = (a, b)$.

\begin{lemma}
  CwF associated to a presheaf category supports $\Sigma$-types.
  \begin{proof}
    Follows after verification of the $\Sigma$-rules. A detailed proof is found
    in \cite{Hofmann}.
  \end{proof}
\end{lemma}
